`phyr`: An R package for model-based phylogenetic analyses

### 2018-10-21 ms.Rmd
complete section heads
Testing pushing to repository. Just added Tony's new leanpub book to references as a test...
update set up

To render the Rmd file into HTML file, go to Terminal, `cd` change directory to the folder of this manuscript, then type `make`. Then you browser should open the file for you after it is done. You can render to MS Word with `make ms.docx` too if you want (I see no reason for this...)

Note about how to insert citation:

1. Go to [Google Scholar](https://scholar.google.com); click the top left, and select `Settings`; then in the `Bibliography manager` section, check `show links to import citations into BibTeX`, then Save it.
2. Back to the Google Scholar homepage and search the paper you want to cite. E.g. "Generalized linear mixed models for phylogenetic analyses of community structure", under the item, click `Import into BibTeX`; then copy the whole new page (`Cmd + A` then `Cmd + C`).

    ```
    @article{ives2011generalized,
      title={Generalized linear mixed models for phylogenetic analyses of community structure},
      author={Ives, Anthony R and Helmus, Matthew R},
      journal={Ecological Monographs},
      volume={81},
      number={3},
      pages={511--525},
      year={2011},
      publisher={Wiley Online Library}
    }
    ```

3. Open the `ref.bib` in this folder, and paste the citation information there.
4. To cite the paper in the manuscript, copy its key (e.g. `ives2011generalized` here), and inset `[@ives2011generalized]` to where you want to cite it. For multiple papers, use `[@key1; @key2]`.
5. That's it.

@@

@@

>>>>

@@

Testing citation of Tony's new book [Dinnage]: [@ives2018book] (BTW, n.p. means No Place, and Author is in place of publisher, since the book is self-published)

@@

# Acknowledgements

# Authors' contributions

# Data Accessibility
